\begin{longtable}{@{}>{\raggedright}p{5.25in} @{} >{\raggedleft}X@{}}

\emph{Talks}  \tabularnewline

\hangindent=5ex \textbf{Spiers, Anna I.}, Brett Melbourne, and Kendi F. Davies. Linked disturbances in Australia: Synergistic impacts of wildfire and forest fragmentation on tree mortality (45 min). Earth Lab Environmental Data Science Seminar. \emph{Remote}. &  2022 \tabularnewline %February

\hangindent=5ex \textbf{Spiers, Anna I.}, Carl Boettiger, Tad Dallas, Nico Franz, Brett A. Melbourne, Kari Norman, Eric Sokol, Thilina Surasinghe, and Kelsey Yule. Forecasting the responses of beetle community metrics (5 min INSPIRE talk). Ecological Society of America Annual Meeting. \emph{Remote Conference}. &  2021 \tabularnewline %August

\hangindent=5ex \textbf{Spiers, Anna I.}, Luis Allende, Kendi F. Davies, Max B. Joseph, Brett A. Melbourne, Christa Torrens, and Grant Vagle. Forecasting carabid distribution shifts with global warming using remote sensing and open source data (5 min lightning talk). Society for Conservation Biology North America Annual Meeting. \emph{Remote Conference}. &  2020 \tabularnewline %August

\hangindent=5ex Victoria Scholl, \textbf{Spiers, Anna I.}, Michael J. Koontz, Megan E. Cattau. Integrating UAS with Airborne Neon Data for Ecological Applications (15 min).  American Society for Photogrammetry and Remote Sensing (ASPRS) Annual Meeting. \emph{Remote Conference}. &  2020 \tabularnewline %June 

\hangindent=5ex \textbf{Spiers, Anna I.} Remote sensing: what can it do for EEB and what resources are at CU Boulder? (45 min). Departmental Lunch and Learn Seminar. &  2019 \tabularnewline %October

\hangindent=5ex \textbf{Spiers, Anna I.} Female Role Models in Mathematical Ecology (30 min). American Association for University Women Boulder Chapter Meeting. &  2019 \tabularnewline %May

\hangindent=5ex \textbf{Spiers, Anna I.}, Kendi F. Davies, Brett A. Melbourne, Megan E. Cattau, and Keith Musselman. Let the Sunshine In: Modeling solar radiation in a fragmented landscape (45 min). Earth Lab Incubator. &  2019 \tabularnewline %May

\hangindent=5ex \textbf{Spiers, Anna I.} The science of Pura Vida: Tropical exploration through the Organization for Tropical Studies (45 min). Departmental Lunch and Learn Seminar. &  2019 \tabularnewline %February

\hangindent=5ex \textbf{Spiers, Anna I.} Habitat Fragmentation (3 min). University of Colorado Student Research Spring Symposium. &  2018 \tabularnewline %April

\hangindent=5ex \textbf{Spiers, Anna I.} and Julie C. Blackwood. Predicting the Future: How to Predict Critical Transitions in Ecological Systems (45 min). Williams College Department of Mathematics Senior Colloquium. &  2014 \tabularnewline %October


\emph{Posters}  \tabularnewline

\hangindent=5ex \textbf{Spiers, Anna I.}, Brett A. Melbourne, and Kendi F. Davies. Synergistic impacts of wildfire and experimental forest fragmentation on tree mortality. Ecological Society of America Annual Meeting. \emph{Remote Conference}. &  2021 \tabularnewline %August

\hangindent=5ex R. Quinn Thomas, Carl Boettiger, Cayelan Carey, Michael Dietze, and 14 more co-authors. Introducing the NEON Ecological Forecasting Challenge hosted by the Ecological Forecasting Initiative Research Coordination Network. American Geophysical Union Annual Meeting. \emph{Remote Conference}. &  2020 \tabularnewline %December

\hangindent=5ex \textbf{Spiers, Anna I.}, Luis Allende, Kendi F. Davies, Max B. Joseph, Brett A. Melbourne, Christa Torrens, and Grant Vagle. NEON: Forecasting carabid beetle dynamics in forests. Ecological Society of America Annual Meeting. \emph{Remote Conference}. &  2020 \tabularnewline %August

\hangindent=5ex \textbf{Spiers, Anna I.}, Megan E. Cattau, Joseph McGlinchy, Brian Johnson, Brett A. Melbourne, and Kendi F. Davies.  Combining UAV remote sensing and ground sensors to model understory solar radiation and thermal habitat in a fragmented forest landscape. Ecological Society of America Annual Meeting. &  2019 \tabularnewline %August

\hangindent=5ex \textbf{Spiers, Anna I.}, Brett A. Melbourne, and Kendi F. Davies.  Combining UAV remote sensing and ground sensors to model understory solar radiation and thermal habitat in a fragmented landscape. Cooperative Institute for Research in Environmental Sciences Annual Rendezvous. &  2019 \tabularnewline %May

\hangindent=5ex \textbf{Spiers, Anna I.}, Jacqueline Wentz, Brett A. Melbourne, and Kendi F. Davies.  The role of \emph{Eucalyptus radiata} in a fragmented landscape. Guild of Rocky Mountain Ecologists and Evolutionary Biologists Annual Meeting. &  2018 \tabularnewline %September

\hangindent=5ex \textbf{Spiers, Anna I.}, Jacqueline Wentz, Brett A. Melbourne, and Kendi F. Davies.  Modeling \emph{Eucalyptus radiata} canopy response to habitat fragmentation. Ecological Society of America Annual Meeting. &  2018 \tabularnewline %August

\end{longtable}
