\begin{longtable}{@{} >{\raggedright}p{5.25in} >{\raggedleft}X @{}}

\hangindent=5ex \textbf{Koontz, Michael J.}, Zachary L. Steel, Andrew M. Latimer, and Malcolm P. North. Initial wildfire suppression efforts select for more extreme fuel and climate burning conditions in Sierra Nevada forests.  & [\textcolor{blue}{\href{https://github.com/mikoontz/selection-by-suppression}{GitHub}}] \tabularnewline

\hangindent=5ex \textbf{Koontz, Michael J.}, Malcolm P. North, Amy DeCastro, Jennifer K. Balch, and Andrew M. Latimer. Fine-scale drivers of California megafires.  & [\textcolor{blue}{\href{https://github.com/mikoontz/megafire-fine-scale-drivers}{GitHub}}] \tabularnewline

\hangindent=5ex Provost, Mikaela, Jan Ng, Jessica Rudnick, Linda Estel\'i M\'endez Barrientos, Steven P. Lee, \textbf{Michael J. Koontz}, and Emilio A. Laca. Novel integration of holistic review and statistical analysis to rank applications in an R1 STEM graduate program. & \tabularnewline

\hangindent=5ex DeCastro, Amy, \textbf{Michael J. Koontz}, and Jennifer K. Balch. Local-scale predictors of fire spread across the U.S. & \tabularnewline

\hangindent=5ex Merchant, Thomas, Elisa Van Cleemput, \textbf{Michael J. Koontz}, and Katherine Suding. Fire-mediated changes in efficiency and sensitivity of net primary productivity in the Great Basin. & \tabularnewline

\hangindent=5ex Huesca, Margarita, \textbf{Michael J. Koontz}, Alexander Koltunov, Yuhan Huang, Andrew M. Latimer, and Yufang Jin. Tree mortality assessment using imaging spectroscopy data in the Sierra Nevada mountains. & \tabularnewline

% \hangindent=5ex DeCastro, Amy, and \textbf{Michael J. Koontz}. Calculating surface area from a broad-extent, fine-grain digital surface model using Google Earth Engine. & \tabularnewline

\end{longtable}



%\hangindent=5ex Emilio A. Laca, Steven P. Lee, Jan Ng, Mikaela M. Provost, Jessica Rudnick, Linda Mendez-Barriento, Derek J. Young, \textbf{Michael J. Koontz}, Anne Todgham, Ben Sacks, and Elizabeth Sturdy. Holistic review in graduate admissions for an R1 STEM program: I. Statistical method to weight desirable applicant qualities and minimize reviewer effects. & \tabularnewline

% these are some collaborations that will hopefully be revived
%\hangindent=5ex \textbf{Michael J. Koontz} and Jeff C. Schank. An agent based model simulation of the outbreak behavior of the western pine beetle during the 2012 to 2016 Sierra Nevada megadrought. & [\textcolor{blue}{\href{https://github.com/mikoontz/wpb-forest-structure-abm}{GitHub}}] \tabularnewline

%\hangindent=5ex Jens T. Stevens, \textbf{Michael J. Koontz}, and Chhaya M. Werner.
%Local effects of aspect on vegetation productivity in California.  & \tabularnewline
%
%\hangindent=5ex \textbf{Michael J. Koontz} and Ruth A. Hufbauer.
%Several, small introductions of individuals to a novel environment facilitate adaptation by mitigating genetic load. & [\textcolor{blue}{\href{https://github.com/mikoontz/ppp-adaptation}{GitHub}}] \tabularnewline





Spiers, A.I., Melbourne, B.A., & Davies, K.F. (in prep). Synergistic impacts of forest fragmentation and wildfire on tree mortality.

also forest survey for British COlombia guy

****AIS SEE NOTES FROM CURRENT RESEARCH WEBPAGE****

