\begin{longtable}{@{}>{\raggedright}p{5.25in} >{\raggedleft}X@{}}
 \addlinespace[1ex]
 
\emph{Undergraduate mentorship}  & \tabularnewline
Hailey Perryman, University of Colorado Boulder (Ecology major). Mentored throughout honors thesis (e.g., primary literature reading, statistics, scientific writing)  & 2022 - 2023 \tabularnewline
Amber Kou, University of Colorado Boulder (Computer Science major). Mentored in satellite image time-series processing in R & 2022 \tabularnewline
Wyatt Metelman-Alvis, University of Colorado Boulder (Ecology major). Mentored throughout honors thesis (e.g., primary literature reading, statistics, scientific writing)  & 2021 - 2022 \tabularnewline
Jacob Hornfeldt, University of Florida (Entomology and Nematology major). Ecological Society of America Meeting SEEDS Program & 2020  \tabularnewline
 \addlinespace[1ex]
 
\emph{Graduate peer mentorship}  & \tabularnewline
Chris Arehart, University of Colorado Boulder (Evolutionary Biology). Mentored for research rotation regarding remote sensing data manipulation & 2021 \tabularnewline
Skylar Lynch, University of Colorado Boulder (Evolutionary Biology). Graduate School Peer Mentorship Program. Offered guidance and support to new graduate students to fulfill the need for mentoring across disciplinary boundaries and to build community among different graduate student populations. & 2019 - 2020 \tabularnewline
Isaiah Tristan, University of Colorado Boulder (Astrophysics). Graduate School Peer Mentorship Program. Offered guidance and support to new graduate students to fulfill the need for mentoring across disciplinary boundaries and to build community among different graduate student populations.  & 2018 - 2019  \tabularnewline
 \addlinespace[1ex]
 
%\emph{Mentee}  & \tabularnewline
%Women in Science and Engineering (WiSE) & 2018 - 2019 \tabularnewline

\end{longtable}


