\begin{longtable}{@{} >{\raggedright}p{6.10in} >{\raggedleft}X @{}}

\hangindent=5ex 6. \textbf{Spiers, Anna I.}, J. Andy Royle, Christa L. Torrens, and Maxwell B. Joseph. (\emph{in press}). Estimating occupancy dynamics and encounter rates with species misclassification: a semi-supervised, individual-level approach. \emph{Methods in Ecology \& Evolution}. https://doi.org/10.1111/2041-210X.13858  &  \tabularnewline

\hangindent=5ex 5. Koontz, Michael J., Victoria Scholl, \textbf{Anna I. Spiers}, Megan E. Cattau, John Adler, Joseph McGlinchy, Tristan Goulden, Brett A. Melbourne, and Jennifer K. Balch. (\emph{in press}). Democratizing macroecology: integrating uncrewed aerial systems with the National Ecological Observatory Network. \emph{Ecosphere}.  &  \tabularnewline

\hangindent=5ex 4. Nagy, Chelsea R., Jennifer K. Balch, and 118 co-authors. 2021. Harnessing the NEON data revolution to advance open environmental science with a diverse and data capable community. \emph{Ecosphere}. 12 (12): e03833. https://doi.org/10.1002/ecs2.3833  &  \tabularnewline

\hangindent=5ex 3. Haefke, Brandon J., \textbf{Anna I. Spiers}, William R. Miller, and Meg D. Lowman. 2014. Tardigrades of the Canopy: \emph{Doryphoribius elleneddiei} nov. sp. (Eutardigrada, Parachela, Hypsibiidae), a New Species from Eastern Kansas, U.S.A. \emph{Transactions of the Kansas Academy of Science}. https://doi.org/10.1660/062.118.0106  &  \tabularnewline

\hangindent=5ex 2. \textbf{Spiers, Anna I.}, Brandon J. Haefke, William R. Miller, and Meg D. Lowman. 2013. Tardigrades in the Canopy: \emph{Doryphoribius dawkinsi} Michalczyk and Kaczmarek, 2010 - New records from eastern Kansas, U.S.A. \emph{Transactions of the Kansas Academy of Science}. 116(3/4):125-128. https://doi.org/10.1660/062.117.0319  &  \tabularnewline

\hangindent=5ex 1. Brandon J. Haefke, \textbf{Anna I. Spiers}, William R. Miller, and Meg D. Lowman. 2013. Tardigrades in the Canopy: Using Double Rope Techniques to Conduct Sampling Along Vertical Transects. \emph{Transactions of the Kansas Academy of Science}. 116(3-4):119-124. https://doi.org/10.1660/062.116.0303  &  \tabularnewline

\end{longtable}
